\ldots

### 2013-06-13 summer13/frac2.tex
nothing really
added blurb about trace

@@

\begin{definition}{(Syntax of {{PiTF}})}
\label{def:PiTF}
%subcode{bnf} include main
% value types, r ::= b / b
% values, f ::= (v |--> v amp c)
%
% iso.~types, t ::= r <=> r
% base iso ::= swap+ | assocl+ | assocr+ 
%     &|& unite | uniti | swap* | assocl* | assocr* 
%     &|& dist | factor 
%     &|& eta | epsilon
% iso comb., c ::= iso | id | sym c | c (;) c | c (+) c | c (*) c 
% top level term, l ::= c v
\end{definition}

>>>>

\section{ {{Pi}} with trace}

In order to take a step toward being able to write the Int construction in
{{Pi}} to give it fractional types, we want to add a trace combinator to it,
with the following type:

%subcode{proof} include main
%@  c : b1 * b <-> b2 * b
%@@ trace c : b1 <-> b2

This kind of combinator allows us to cancel out a common factor. When the type
{{0}} is removed from the language, it is always possible to do this, but adding
computational content becomes tricky. For example, consider permutations on the
finite set of size {{6}}. If we wish to trace one of these to get a permutation
on the set of size {{3}}, we are able to, but which set of size {{3}}? There
are several different ways to do this, but there is no obvious canonical answer.

More concretely, suppose we have a combinator {{c : 3 * 2 <-> 3 * 2}}. The
combinator {{trace c : 3 <-> 3}} can be constructed in two obvious ways: let
{{(trace c) v}} run {{c}} on {{(v, true)}} or on {{(v, false)}}. It is possible
to choose {{c}} so that depending on which default value of type {{2}} is used,
a different combinator results.

To fix this, we parameterize {{trace}} with a value {{v : b}}, as follows:

%subcode{proof} include main
%@  c : b1 * b <-> b2 * b
%@  v : b
%@@ trace_v c : b1 <-> b2

It remains to show that this is ``well-behaved''; that is, we want it to obey
some (ideally all) of the trace properties, or at the very least some subset of
them that is sufficient to prove some necessary properties for {{Pi}} extended
with fractional types, as presented in the next few sections.

@@

\begin{definition}{(Syntax of {{PiTF}})}
\label{def:PiTF}
%subcode{bnf} include main
% value types, r ::= b1 / b2
% values, f ::= (v1 |--> v2, c)
%
% iso.~types, t ::= r <=> r
% base iso ::= swap+ | assocl+ | assocr+ 
%     &|& unite | uniti | swap* | assocl* | assocr* 
%     &|& dist | factor 
%     &|& eta | epsilon
% iso comb., c ::= iso | id | sym c | c (;) c | c (+) c | c (*) c 
% top level term, l ::= c v
\end{definition}
